Verifying Demonstrations

### 2020-03-11 paper/DB-Schnorr-UWB.tex
Renames label for DBS-UWB figure
Fixes error in UWB MF proof

We present the protocol in \cref{SchnorrFigure}.
The (cyclic) group with generator \(g\) and order \(q\) are system parameters.
The private key \(\alpha\) with public key \(A = g^\alpha\) are generated once by the prover in the setup phase.
Let \(\UWBPR\) be the protocol of \textcite{UWBPR}.
Further, let
\(\UWBPRsend[_k][m]\) denote sending a message~\(m\) with the shared key~\(k\),
\(m'\gets \UWBPRrecv_k\) denote receiving a message~\(m'\) with shared 
key~\(k\) and finally
\(\Delta t\gets \UWBPRtime\) denote the time between the last \(\UWBPRsend\) 
and \(\UWBPRrecv\) operations.

@@

  \end{tabular}
  \caption{%
    One-round protocol instance of the \(\DBSprove\leftrightarrow \DBSverify\) 
    protocol instantiating \(\PK[\alpha][A = g^\alpha]\).
    Each transmission (arrow in the diagram) uses \(\UWBPR\).
    The protocol should be repeated \(n\) times to achieve the desired 
    soundness and distance-bounding errors.
  }%
  \label{SchnorrFigure}
\end{figure*}

@@

\begin{theorem}[\acs*{DBMF} resistance]
  Let \(\adv\) be a \((t, \qobs, \qp, \qv)\)-MF adversary, then 
  \(\Adv_{\DBS}^{\text{MF}}(\adv) = \left(\frac{1}{m}+\frac{1}{q}\right)^n\), 
  where \(m, q\) are as in \cref{DB-Schnorr}.
\end{theorem}

@@

  The total success probability is \(\frac{1}{m} + \frac{1}{q}\) per round, 
  thus \(\left(\frac{1}{m}+\frac{1}{q}\right)^n\) in total per protocol 
  session.
\end{proof}

@@

The setup phase is similar to \(\DBS\) (\cref{SchnorrFigure}).
They use the agreed upon key~\(k = \gDH^{\xDH \yDH}\) as the key for 
\(\UWBPR\), instead of a static \(k\).
\(\DBS\) performs \(
  \PK[\alpha][A = g^\alpha]
\) (with a distance bound) whereas \(\DBSHW\) must perform \[
  \PK[\alpha, \xDH, \sk_P, \sigma][
    A = g^\alpha \land
    \XDH = \gDH^{\xDH} \land
    \Blind[\sigma] = \Sign[_{\sk}][\sk_P]
  ].
\] This means that the prover (and verifier) must prepare for the other proofs 
too.

@@

\(\XDHCL = \XDH^{\sk}\) is simply a representation of \(\sk\) in a randomly 
chosen base~\(\XDH\).
If an adversary can use this to tell one device from another, then the 
adversary can solve the \ac{DDH} problem.
Consider the following reduction.

>>>>

We present the protocol in \cref{DB-Schnorr-UWB-figure}.
The (cyclic) group with generator \(g\) and order \(q\) are system parameters.
The private key \(\alpha\) with public key \(A = g^\alpha\) are generated once by the prover in the setup phase.
Let \(\UWBPR\) be the protocol of \textcite{UWBPR}.
Further, let
\(\UWBPRsend[_k][m]\) denote sending a message~\(m\) with the shared key~\(k\),
\(m'\gets \UWBPRrecv_k\) denote receiving a message~\(m'\) with shared 
key~\(k\) and finally
\(\Delta t\gets \UWBPRtime\) denote the time between the last \(\UWBPRsend\) 
and \(\UWBPRrecv\) operations.

@@

  \end{tabular}
  \caption{%
    One-round protocol instance of the \(\DBSprove\leftrightarrow \DBSverify\) 
    protocol instantiating \(\PK[\alpha][A = g^\alpha]\).
    Each transmission (arrow in the diagram) uses \(\UWBPR\).
    The protocol should be repeated \(n\) times to achieve the desired 
    soundness and distance-bounding errors.
  }%
  \label{DB-Schnorr-UWB-figure}
\end{figure*}

@@

\begin{theorem}[\acs*{DBMF} resistance]
  Let \(\adv\) be a \((t, \qobs, \qp, \qv)\)-MF adversary, then 
  \(\Adv_{\DBS}^{\text{MF}}(\adv) = \frac{1}{m^n}\), where \(m\) is as in 
  \cref{DB-Schnorr}.
\end{theorem}

@@

  Since \(m \leq q\), the best strategy is to guess which challenge the 
  verifier will use.
  Thus, the total success probability is \(\frac{1}{m^n}\).
\end{proof}

@@

The setup phase is similar to \(\DBS\) (\cref{DB-Schnorr-UWB-figure}).
They use the agreed upon key~\(k = \gDH^{\xDH \yDH}\) as the key for 
\(\UWBPR\), instead of a static \(k\).
\(\DBS\) performs \(
  \PK[\alpha][A = g^\alpha]
\) (with a distance bound) whereas \(\DBSHW\) must perform \[
  \PK[\alpha, \xDH, \sk_P, \sigma][
    A = g^\alpha \land
    \XDH = \gDH^{\xDH} \land
    \Blind[\sigma] = \Sign[_{\sk}][\sk_P]
  ].
\] This means that the prover (and verifier) must prepare for the other proofs 
too.

@@

To answer the second question,
\(\XDHCL = \XDH^{\sk}\) is simply a representation of \(\sk\) in a randomly 
chosen base~\(\XDH\).
If an adversary can use this to tell one device from another, then the 
adversary can solve the \ac{DDH} problem.
Consider the following reduction.
